---
title: "Mission Hospital"
author: "Debdutta Roy Exe-Weekend 2019-2020"
date: "18/04/2020"
output:
  word_document: default
  pdf_document: default
---


```{r }

library(readxl)  # install.packages("readxl") or install.packages("tidyverse")

library(plyr)

library(tibble)
#install.packages("Hmisc")
library("Hmisc")
#install.packages("corrplot")
library(corrplot)
library(ppcor)
library(MASS)

xl_data <- "/Users/debduttaroy/Documents/r-program/midtermassignmentsstatisticswithrsemesterie/IMB529-XLS-ENG.xlsx"
library(stats)


excel_sheets(path = xl_data)
mh_data <- read_excel(path = xl_data, sheet = "MH-Raw Data") 
#View(mh_data)
mh_mod_data <- read_excel(path = xl_data, sheet = "MH-Modified Data") 
#View(mh_mod_data)

str(mh_mod_data)


```
##summary of the Modified Sheet Data

```{r}
summary(mh_mod_data)
```

##Plotted a graph to show patient arriving with different ailments 

```{r}
mod.df <- data.frame(mh_mod_data$`KEY COMPLAINTS -CODE`)
plot(mod.df,las = 2,cex.axis = .7,cex = .7,main = "Key Complaints",ylim = c(0,60) ,  col=c(1:13))
#majority patient admitted for other heart disease

```

## Modification of the dataset to get correlation between different variables. All fields having character values has other datatypes have been excluded


```{r}
copy_mh <- data.frame(mh_mod_data)
copy_mh$PAST.MEDICAL.HISTORY.CODE[is.na(copy_mh$PAST.MEDICAL.HISTORY.CODE)] <- "None"

copy_mh$PAST.MEDICAL.HISTORY.CODE <- as.factor(copy_mh$PAST.MEDICAL.HISTORY.CODE)
copy_mod_mh <- copy_mh[,c(-1,-4,-6,-8:-20,-28:-33,-38,-39,-41,-43,-45,-50)] #all categorical variables are not considered

copy_mod_mh_na<-na.omit(copy_mod_mh)
#View(copy_mod_mh_na)

copy_mod_mh_na$BP.LOW <- as.numeric(copy_mod_mh_na$BP.LOW)
copy_mod_mh_na.1 <- data.frame(copy_mod_mh_na[,c(-2:-4,-11,-15:-17)])
copy_mod_mh_na.2 <- data.frame(copy_mod_mh_na.1[,c(-15)])
str(copy_mod_mh_na.2)

cor_mhdata <- cor(copy_mod_mh_na.2)
cor_mhdata


```
##To get highly correlated data 

```{r}
corrplot(cor_mhdata, tl.cex = 0.6/par("cex"),
    cl.cex = 0.6/par("cex"))
```

##From plot we can find high correlation between BP-High to Age
```{r}

highly_correlated <- findCorrelation(cor_mhdata , cutoff = 0.6 , names = TRUE)
print(highly_correlated)


```

## Regression between two of the highly correlated variables

```{r}
mission.1 <-lm(copy_mod_mh_na.2$TOTAL.COST.TO.HOSPITAL ~ copy_mod_mh_na.2$AGE)
mission.1$coefficients

plot(copy_mod_mh_na.2$AGE,copy_mod_mh_na.2$TOTAL.COST.TO.HOSPITAL,main = "Total Cost towards Age", xlab = "Age",ylab = "Total cost to Hospital",col = "blue",pch = 20 ) + abline (mission.1$coefficients,col = "red")

```

## Regression between two of the correlated variables.

```{r}
mission.2 <-lm(copy_mod_mh_na.2$TOTAL.COST.TO.HOSPITAL ~ copy_mod_mh_na.2$TOTAL.LENGTH.OF.STAY)
mission.2$coefficients

plot(copy_mod_mh_na.2$TOTAL.LENGTH.OF.STAY ,copy_mod_mh_na.2$TOTAL.COST.TO.HOSPITAL,main = "Total Cost to Total stay", xlab = "Total length of stay including ICU",ylab = "Total cost to Hospital",col = "blue",pch = 20 ) + abline (mission.2$coefficients,col = "red")


```
```{r}
wt <- copy_mod_mh_na.2$BODY.HEIGHT/100
bmi <- copy_mod_mh_na.2$BODY.WEIGHT/(wt)^2

copy_mod_mh_na.3 <- cbind(copy_mod_mh_na.2,bmi)

summary(lm(copy_mod_mh_na.3$TOTAL.COST.TO.HOSPITAL ~ copy_mod_mh_na.3$AGE+copy_mod_mh_na.3$bmi+copy_mod_mh_na.3$TOTAL.LENGTH.OF.STAY+copy_mod_mh_na.3$BP..HIGH+copy_mod_mh_na.3$CREATININE),data = copy_mod_mh_na.3)


```

## Anova between different variables to Total cost to Hospital

```{r}
summary(aov(copy_mod_mh_na.3$TOTAL.COST.TO.HOSPITAL ~ copy_mod_mh_na.3$AGE+copy_mod_mh_na.3$bmi+copy_mod_mh_na.3$TOTAL.LENGTH.OF.STAY+copy_mod_mh_na.3$BP..HIGH+copy_mod_mh_na.3$CREATININE))

```

Here age and total length of stay has very less p value which means it rejects null hypothesis.



